Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-08 referee.tex
Added some answers to simulation questions (not finished yet)

\begin{referee}
The initialization at z=130 is very late. I am aware that it is impossible to 
repeat this simulation starting at an earlier redshift, but would advise for 
future work.
\end{referee}
-Personal question: why is this initialization late?

\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}
-Simulation question

\begin{referee}
What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
\end{referee}
-Simulation question

\begin{referee}
Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
\end{referee}
-Simulation question

@@

-Added a vertical line at $10^5 M_{\odot}$. Detail also added to caption.
-Tried plotting the HMF of the earliest Pop III formation redshift, but I need to collect the HMF of that dataset -- having troubles remembering how this was produced

>>>>

\begin{referee}
The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
\end{referee}

In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.  The maximum baryon overdensity is 1.64$\bar{\rho}_{\rm b}$, and the maximum DM particle displacement is 2.5 $\times$ (cell width).  In future studies, we will start at earlier times when the evolution is solidly in the linear regime.  We thank the referee for pointing this out.

\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}

We chose this metallicity threshold based on the work of Omukai et al. (2005), Schneider et al. (2006) and others, who found that dust cooling was efficient enough above this metallicity to induce low-mass star formation.  Very few stars (\textbf{calculate percentage}) form with metallicities between zero and $5 \times 10^{-6} Z_\odot$ and doesn't affect our results greatly.  Stars only obtain this extremely low (non-zero) metallicity when metal mixing is incomplete.  This usually occurs when a blastwave is mixing into a nearby halo, and the core collapses before it can fully mix.  Because of the randomness of the IMF sampling and errors from numerical diffusion and other solvers, we do not place great emphasis on stars in this metallicity range.  It is unclear what would be the actual stellar metallicity when it reaches main sequence, given our 0.1 proper pc resolution.  Thus we have not changed the manuscript on this topic.

\begin{referee}
What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
\end{referee}

We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12.  This density can be calculated as \textbf{(give calculation and density value at level 13)}.

\begin{referee}
Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
\end{referee}

@@

-Added a vertical line at $10^5 M_{\odot}$. Detail also added to caption.
2-Tried plotting the HMF of the earliest Pop III formation redshift, but I need to collect the HMF of that dataset -- having troubles remembering how this was produced
